---
title: "p8105_hw5_jc5457"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Due date

Due: November 16 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |
| Optional survey | No points |


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 


## Problem 2

The Washington Post collected data on more than 52,000 criminal homicides over the past decade in 50 of the largest American cities.

```{r}
homicide_df = read.csv("./data/homicide-data.csv", na = c("","Unknown"))
```

Describe the raw data: 

This dataset contains `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns.
The variable names in this dataset are: 
`r names(homicide_df)`.

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df =
  homicide_df %>% 
  mutate(city_state = str_c(city,state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved")
         ) %>%
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
count(homicide_df, disposition)
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object `baltimore_test`, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
    )

baltimore_test %>% 
  broom::tidy()
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of `purrr::map`, `purrr::map2`, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city (`results_df`).

* write a prop test function
```{r}
prop_test_fuction = function(city_df){
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
      )
  
  return(city_test)
}
```

* Iterate across city
```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_fuction),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

results_df
```

Create a plot that shows the estimates and CIs for each city – check out `geom_errorbar` for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust =1))
```



## Problem 3

Conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

* Fix n=30
* Fix σ=5

Set μ=0. Generate 5000 datasets from the model.
x∼Normal[μ,σ]

```{r}
sample = rerun(5000, rnorm(n = 30,mean = 0,sd = 5))
```

* Write t test function
```{r}
t_test = function(mu = 0) {
  sample = tibble(rnorm(n = 30, mean = mu, sd = 5))
  
  result = t.test(sample) %>% 
    broom::tidy() %>% 
    select(estimate,p.value)
  
  result
}
```

* Apply t test function to the 5000 samples (mean = 0)

For each dataset, save μ̂  and the p-value arising from a test of H:μ=0 using α=0.05.
```{r}
mean_0 = expand_grid(mean = 0, iteration = 1:5000) %>% 
  mutate(result = map(mean,t_test)) %>% 
  unnest(result)
dim(mean_0)
head(mean_0)
```

* Repeat the above for μ={1,2,3,4,5,6}
```{r}
mean_6 = expand_grid(mean = 1:6, iteration = 1:5000) %>% 
  mutate(result = map(mean,t_test)) %>% 
  unnest(result)
dim(mean_6)
head(mean_6)
```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. 
```{r}
mean_6 %>%
  group_by(mean) %>% 
  summarize(proportion_rejected = sum(p.value < 0.05)/5000) %>% 
  ggplot(aes(x = mean,y = proportion_rejected)) +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  geom_point() + geom_path() +
  labs(x = "True Mean",y = "Power",title = "Power of t.test vs. True Means")
```

From the plot, we can see that the association between effect size and power is:

1. When true mean (effect size) increases, power (proportion of rejection) also increases.

2. The speed of power's increase (slop of the plot) slower down as true mean increases.


Make a plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis. 

```{r}
mean_6 %>%
  group_by(mean) %>% 
  summarize(average_estimate = mean(estimate,na.rm = T)) %>% 
  ggplot(aes(x = mean,y = average_estimate)) +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) + 
  geom_point() + geom_path() +
  labs(x = "True Mean",y = "Average Estimate Mean",title = "Estimated Means")
```


Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. 

```{r}
rejected_estimate <- mean_6 %>% 
  filter(p.value < 0.05) %>% group_by(mean) %>% 
  summarize(average_estimate = mean(estimate,na.rm = T)) %>% 
  ungroup()

full_estimate <- mean_6 %>% 
  group_by(mean) %>% 
  summarize(average_estimate = mean(estimate,na.rm = T)) %>% 
  ungroup()
  
ggplot(full_estimate,aes(x = mean, y = average_estimate)) +
  geom_line(data = full_estimate,aes(colour = "blue")) +
  geom_line(data = rejected_estimate,aes(colour = "red")) +
  scale_color_manual(name = " ", values = c("blue" = "blue", "red" = "red"),
                     labels = c('All Estimates','Rejected Estimates'))+
  geom_point(data = full_estimate,colour = "blue") +
  geom_point(data = rejected_estimate,colour = "red") +
  scale_x_continuous(limits = c(1,6), breaks = seq(1,6,1)) +
  labs(x = "True Mean",y = "Average Estimate Mean",title = "All vs. Rejected Estimates")
```

From the plot, we can see that:

1. When the effect size is less than 4, the sample average of μ̂ when the null is rejected is very different from (and always larger than) the true value of μ.

2. When the effect size is larger than 4, the sample average of μ̂ when the null is rejected is approximately equal to the true value of mu. That’s because as the power is increasing.

Conclusion: Given the small sample size and low power, and given that the null is rejected, we can see the average is very different from the true mean. It indicates the publication bias. We should be careful of this situation. When the power is low, the sample size is small, the results that the null is rejected may be far away from the truth.




